\documentclass[11pt, a4paper]{article}

% --- Packages ---
\usepackage[top=2.2cm, bottom=2.2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontenc}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{mdframed}

% --- Colours ---
\definecolor{accent}{RGB}{30, 80, 140}
\definecolor{lightgray}{RGB}{245, 245, 245}
\definecolor{rulecolor}{RGB}{180, 180, 180}

% --- Hyperref setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent,
    pdftitle={Computational Physics Portfolio},
    pdfauthor={Mohak Das}
}

% --- Section formatting ---
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}
  {0em}
  {}[\vspace{-0.4em}\textcolor{rulecolor}{\rule{\linewidth}{0.5pt}}]

\titlespacing{\section}{0pt}{1.4em}{0.6em}

% --- Header/Footer ---
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\small\textcolor{gray}{Computational Physics Portfolio \quad|\quad Mohak Das \quad|\quad Jadavpur University}}
\fancyfoot[R]{\small\textcolor{gray}{\thepage}}

% --- Table column types ---
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

% --- Highlighted box ---
\newmdenv[
  backgroundcolor=lightgray,
  linecolor=rulecolor,
  linewidth=0.5pt,
  innerleftmargin=10pt,
  innerrightmargin=10pt,
  innertopmargin=8pt,
  innerbottommargin=8pt,
  skipabove=0.5em,
  skipbelow=0.5em
]{infobox}

% ============================================================
\begin{document}
% ============================================================

% --- Title block ---
\begin{center}
  {\LARGE\bfseries\color{accent} Computational Physics Portfolio}\\[0.5em]
  {\large Mohak Das}\\[0.2em]
  {\normalsize M.Sc. Physics (First Year) \quad|\quad Jadavpur University \quad|\quad 2025--26}\\[0.2em]
  {\small \href{mailto:mohakdas06@proton.me}{mohakdas06@proton.me}
  \quad|\quad 8961576662}
\end{center}

\vspace{0.5em}
\textcolor{rulecolor}{\rule{\linewidth}{1pt}}
\vspace{0.8em}

% --- Overview ---
\begin{infobox}
\textbf{About this portfolio.}
This repository collects all assignments from a dedicated Computational Physics
course. Each assignment is self-contained with modular Fortran~90 source code,
a compiled PDF report written in \LaTeX, and plotting scripts (Python or
Gnuplot). The assignments span five domains: \textit{Nonlinear Dynamics}, \textit{Molecular
Dynamics}, \textit{Monte Carlo Methods}, \textit{Finite Difference Methods}, and the \textit{WKB
approximation}. All numerical integrators and solvers are implemented from
scratch without external scientific libraries.
\end{infobox}

\vspace{0.3em}

% --- Assignment Overview Table ---
\section{Assignments at a Glance}

\renewcommand{\arraystretch}{1.45}
\begin{tabularx}{\linewidth}{C{0.5cm} L{3.2cm} L{4.8cm} L{3.5cm} C{1.2cm}}
  \toprule
  \textbf{\#} & \textbf{Assignment} & \textbf{Key Problems} & \textbf{Methods} & \textbf{Lang.} \\
  \midrule

  1 &
  Nonlinear Dynamics \newline\texttt{NLD\_Assignment/} &
  Simple pendulum, Lotka--Volterra,
  Lorenz attractor, quartic oscillator,
  saddle--centre system &
  RK5 integration, phase portraits,
  vector fields, strange attractors &
  F90 + Gnuplot \\

  2 &
  Molecular Dynamics \newline\texttt{MD\_Simulation/} &
  Lennard-Jones N-body simulation,
  energy conservation, velocity
  distribution, equilibration &
  Velocity Verlet integrator,
  periodic BCs, Microcanonical (NVE) ensemble &
  F90 + Gnuplot \\

  3 &
  Monte Carlo \newline\texttt{MC\_Simulation/} &
  Numerical estimation of area under curves and volume under surfaces &
  Sampling method, Mean-value method &
  F90 + Gnuplot \\

  4 &
  Finite Difference Method \newline\texttt{FDM\_Assignment/} &
  1D Schr{\"o}dinger equation for
  14 quantum potentials (harmonic,
  Morse, double well, Dirac delta, \ldots) &
  FDM matrix diagonalisation,
  eigenvalue problems &
  F90 + Python \\

  5 &
  WKB Approximation \newline\texttt{WKB\_Assignment/} &
  Numerical estimation of eigen energies of various slowly varying 1D potentials &
  Trapezoidal, Bisection Method. &
  F90  \\

  \bottomrule
\end{tabularx}

\vspace{0.5em}

% --- Technical Skills ---
\section{Technical Highlights}

\begin{itemize}[leftmargin=1.4em, itemsep=0.3em]

  \item \textbf{Modular Fortran~90.}
  Shared solver modules (\texttt{RK5\_solver.f90}, \texttt{FDM\_toolbox.f90},
  \texttt{constants\_mod.f90}) are written as reusable Fortran modules and
  linked against multiple problem programs. No solver code is duplicated across
  files.

  \item \textbf{Build system.}
  Each assignment has a \texttt{Makefile} managing compilation dependencies.
  Assignments with separate plotting pipelines use a second
  \texttt{Makefile.plots}.

  \item \textbf{Reproducible pipeline.}
  The chain from source to figure is fully reproducible:
  \texttt{.f90} $\to$ executable $\to$ output data $\to$ plotting script
  $\to$ \texttt{.pdf} figure $\to$ \LaTeX\ report. No manual steps are
  required between stages.

  \item \textbf{Documentation.}
  Every assignment contains a \texttt{README.md} describing the physical
  problem, folder structure, build instructions, and dependencies.
  Reports are written in \LaTeX\ with full derivations, result tables,
  and discussion.

\end{itemize}

% --- Repository Structure ---
\section{Repository Structure}

\begin{infobox}
\ttfamily\small
\begin{tabbing}
Computational\_Physics\_Portfolio/ \\
\hspace{1.5em}\=README.pdf \hspace{3em} \=\textrm{$\leftarrow$ this document}\\
\>NLD\_Assignment/ \>\textrm{Nonlinear dynamics}\\
\>MD\_Simulation/ \>\textrm{Molecular dynamics}\\
\>MC\_Simulation/ \>\textrm{Monte Carlo methods}\\
\>FDM\_Assignment/ \>\textrm{Finite difference methods}\\
\>WKB\_Assignment/ \>\textrm{WKB approximation}\\
\end{tabbing}
\end{infobox}

Each subdirectory follows the same internal convention:\\[0.3em]
\hspace*{1.5em}\texttt{src/} — Fortran source \quad
\texttt{plots/} — Generated figures \quad
\texttt{gnuplot/} or \texttt{scripts/} — Plotting pipeline\\
\hspace*{1.5em}\texttt{Makefile} — Build system \quad
\texttt{README.md} — Usage instructions \quad
\texttt{[Name].pdf} — Report

% --- Dependencies ---
\section{Dependencies}

\begin{tabularx}{\linewidth}{L{3.5cm} L{4cm} X}
  \toprule
  \textbf{Tool} & \textbf{Version} & \textbf{Used in} \\
  \midrule
  \texttt{gfortran}   & $\geq$ 9.0  & All assignments \\
  \texttt{Python}     & $\geq$ 3.8  & FDM (matplotlib, numpy) \\
  \texttt{Gnuplot}    & $\geq$ 5.4  & NLD, MD, MC \\
  \LaTeX\ (pdflatex)  & Any recent  & All reports \\
  \bottomrule
\end{tabularx}

\vspace{1.5em}
\textcolor{rulecolor}{\rule{\linewidth}{0.5pt}}
\begin{center}
  \small\textcolor{gray}{All work is original. Programs were written and tested
  on [OS, e.g. Linux/Ubuntu 24.04].
  \quad Repository last updated: \today}
\end{center}

\end{document}
